Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-06-28 main_revision.tex

Root:leaf ratio (\emph{froot\_leaf}) has 1) a direct effect on LAI, via changes in tissue allocation fractions , 2) an indirect effect on NPP, via changes in maintenance costs of fine root pools, 3) an effect on the uptake of water via root biomass and 4) an effect on nutrient limitation through root-mediated N uptake costs.  The first two impacts decrease NPP with higher \emph{froot\_leaf} costs and the latter two increase it via \emph{froot\_leaf} benefits. CAX and NWR exhibit higher LAI with fewer roots, HVF exhibits lower LAI with fewer roots, and MET

Both types of effect are seen here, with the Niwot Ridge and Metolius sites (which have the lowest productivity and LAI, and thus presumably very low root biomass in the first place) suffering very large reductions in GPP, NPP, and LAI at low \emph{froot\_leaf} ratios, reflecting mechanisms 3 and 4.  Harvard forest and Caxiuan\~a both show increases in all variables with low \emph{froot\_leaf}.  In Figure \ref{btran state}, we can see that low \emph{froot\_leaf} is a primary control over drought stress at Metolius, in particular.

Low values of \emph{stem\_leaf} ratio typically resulted in much higher LAI at all sites, as well as declines in vegetation carbon, as expected from the lower stem carbon allocation. At Niwot Ridge, there is an optimum (or local maximum) stem carbon observed, due to the impacts of a too-high leaf area index, which caused declines in NPP at low \emph{stem\_leaf}. At all other sites, the impact of increasing leaf allocation is to increase NPP (almost doubling at Metolius). Decreases in stem:leaf ratio also caused a decline in leaf N per unit area, potentially on account of the higher demand for N uptake and thus higher N limitation. This effect is llustrated clearly for Niwot Ridge and Metolius in Figure \ref{btran state}).

>>>>

Root:leaf ratio (\emph{froot\_leaf}) has 1) a direct effect on LAI, via changes in tissue allocation fractions , 2) an indirect effect on NPP, via changes in maintenance costs of fine root pools, 3) an effect on the uptake of water via root biomass and 4) an effect on nutrient limitation through root-mediated N uptake costs.  The first two impacts decrease NPP with higher \emph{froot\_leaf} costs and the latter two increase it via \emph{froot\_leaf} benefits. CAX and HVF exhibit higher LAI with fewer roots.   NWR has large reduction in LAI (and GPP & NPP) with fewer roots. MET exhibits a mixed response crossing an optimal value. \emph{froot\_leaf} is a primary control over drought stress at both NWR and MET ( Figure \ref{btran state}).

Low values of \emph{stem\_leaf} ratio resulted in higher LAI at all sites, as well as declines in total vegetation carbon. At Niwot Ridge, there is an optimum (or local maximum) stem carbon observed, due to the impacts of a too-high leaf area index, which caused declines in NPP at low \emph{stem\_leaf}. At all other sites, the impact of increasing leaf allocation is to increase NPP (almost doubling at Metolius). Decreases in stem:leaf ratio also caused a decline in leaf N per unit area, potentially on account of the higher demand for N uptake and thus higher N limitation. This effect is llustrated clearly for Niwot Ridge and Metolius in Figure \ref{btran state}).
